---
title: "Processing"
---

```{r setup, include=FALSE}

# Do not echo code chunks in rendered document

knitr::opts_chunk$set(echo = FALSE);

# Do not render values returned by code in code chunks

knitr::opts_chunk$set(results = "hide")

# Clear the global environment

rm(list = ls());

# Create an environment to hold metadata to be transferred to later scripts

metaEnv <- new.env();

```

<!-- Automatically populate a description of the compilation of this file. -->

Generated from R markdown file **./02_Protocol/`r knitr::current_input()`**, last compiled on `r Sys.time()`

```{r}

# Make sure target directories exist.

tempPath <- "./03_incremental/temp";
dir.create(
  path = tempPath,
  recursive = TRUE,
  showWarnings = FALSE
);
productPath <- "./04_product";
dir.create(
  path = productPath,
  recursive = TRUE,
  showWarnings = FALSE
);

```

## EEMS reference table

Create the table of references to the file names of the EEMS matrix files in the accompanying zip file.

```{r}

# Read the R data file with the vector of EEMS file names

eemsFilenames <- readRDS(file = "./03_incremental/temp/eemsFilenames.RData");

# Split the filenames into a matrix of metadata about the sample date,
# site ID, and replicate ID

eemsNamesMatrix <- sapply(
  X = strsplit(
    x = as.character(strsplit(x = eemsFilenames$new, split = ".csv$")), 
    split = "_",
    fixed = TRUE
  ),
  FUN = function(x) {
    return( 
      c(
        x[1], 
        substring(text = x[2], first = 2, last = nchar(x[2])), 
        substring(text = x[3], first = 2, last = 2)
      ) 
    );
  }
);

# Specify the table metadata

metaEnv$tableEEMSFiles.name <- "EEMS_wy2018_Aqualog";

metaEnv$tableEEMSFiles.desc <- paste(
  "References to comma delimited text files with",
  "analysis-ready excitation-emission matrices (EEMS)",
  "from fluorometric analysis of dissolved organic carbon",
  "sampled in triplicate along the Upper Clark Fork River." 
);

# Read the project attributes table
# and restructure for convenience.

atts <- as.data.frame(
  t(as.matrix(
    readxl::read_excel(
      path = "./01_input/meta/attributes.xlsx",
      sheet = "attributes",
      range = readxl::cell_limits(ul = c(2, 3)),
      col_names = TRUE,
      col_types = rep("text", times = 10)
    )
  ))
);
names(atts) <- readxl::read_excel(
  path = "./01_input/meta/attributes.xlsx",
  sheet = "attributes",
  range = readxl::cell_limits(ul = c(3, 2), lr = c(NA, 2)),
  col_names = "rownames",
  col_types = "text"
)$rownames;
atts[is.na(atts)] <- "";

metaEnv$tableEEMSFiles.meta <- data.frame(
  dateString = atts$date,
  siteID = atts$siteID,
  repID = atts$repID,
  eemsFile = atts$eemsFileRef,
  row.names = rownames(atts)
);

# Create the data frame that contains the table of references to EEMS
# matrix files.

eemsTable <- data.frame(
  eemsNamesMatrix[1,],
  eemsNamesMatrix[2,],
  eemsNamesMatrix[3,],
  sprintf(
    "EEMS_wy2018_Aqualog.zip/%s",
    eemsFilenames$new
  )
);
colnames(eemsTable) <- names(metaEnv$tableEEMSFiles.meta);

# Create a numerical dates to determine earliest and latest dates for metadata

dates <- as.POSIXct(eemsTable$dateString, format = "%Y%m%d", tz = "UTC");
metaEnv$startTime <- min(dates);
metaEnv$endTime <- max(dates);

metaEnv$sites <- sort(unique(eemsTable$siteID));

```

`r sprintf("**%s.csv**", metaEnv$tableEEMSFiles.name)`: `r metaEnv$tableEEMSFiles.desc`

`r knitr::kable(x = metaEnv$tableEEMSFiles.meta) `

```{r}

# Write the data table to the product

write.csv(
  x = eemsTable,
  file = sprintf(
    "%s/%s.csv",
    productPath,
    metaEnv$tableEEMSFiles.name
  ),
  row.names = FALSE
)

```

Data table written to `r sprintf("./%s.csv", metaEnv$tableEEMSFiles.name) `


## Table to define wavelengths for EEMS excitations

Create the table of column numbers and associated wavelengths

```{r}

ExMax <- 450;
ExMin <- 250;
ExRes <- 5;
table <- data.frame(
  colNum = 1:(((ExMax - ExMin) / ExRes) + 1),
  ExWavelength = seq(from = ExMin, to = ExMax, by = ExRes)
)

# Specify the table metadata

metaEnv$tableEEMSCols.name <- "EEMS_excitation_wavelengths";

metaEnv$tableEEMSCols.desc <- 
  "Wavelenths for excitation (columns left to right) in EEMS matrices";

metaEnv$tableEEMSCols.meta <- data.frame(
  colNum = atts$matrixColNum,
  ExWavelength = atts$eemsExcitationWavelength,
  row.names = rownames(atts)
);

```

`r sprintf("**%s.csv**", metaEnv$tableEEMSCols.name)`: `r metaEnv$tableEEMSCols.desc`

`r knitr::kable(x = metaEnv$tableEEMSCols.meta) `

```{r}

# Write the data table to the product

write.csv(
  x = table,
  file = sprintf(
    "%s/%s.csv",
    productPath,
    metaEnv$tableEEMSCols.name
  ),
  row.names = FALSE
)

```

Data table written to `r sprintf("./%s.csv", metaEnv$tableEEMSCols.name) `


## Table to define wavelengths for EEMS emissions

Create the table of row numbers and associated wavelengths

```{r}

EmMax <- 560;
EmMin <- 300;
EmRes <- 2;
table <- data.frame(
  rowNum = 1:(((EmMax - EmMin) / EmRes) + 1),
  EmWavelength = seq(from = EmMin, to = EmMax, by = EmRes)
)

# Specify the table metadata

metaEnv$tableEEMSRows.name <- "EEMS_emission_wavelengths";

metaEnv$tableEEMSRows.desc <- 
  "Wavelenths for emissions (rows top to bottom) in EEMS matrices";

metaEnv$tableEEMSRows.meta <- data.frame(
  rowNum = atts$matrixRowNum,
  EmWavelength = atts$eemsEmissionWavelength,
  row.names = rownames(atts)
);

```

`r sprintf("**%s.csv**", metaEnv$tableEEMSRows.name)`: `r metaEnv$tableEEMSRows.desc`

`r knitr::kable(x = metaEnv$tableEEMSRows.meta) `

```{r}

# Write the data table to the product

write.csv(
  x = table,
  file = sprintf(
    "%s/%s.csv",
    productPath,
    metaEnv$tableEEMSRows.name
  ),
  row.names = FALSE
)

```

Data table written to `r sprintf("./%s.csv", metaEnv$tableEEMSRows.name) `


## Table of absorbances of all excitation wavelengths

```{r}

metaEnv$tableAbsorbance.name <- "Absorbance_wy2018_Aqualog";

metaEnv$tableAbsorbance.desc <- paste(
  "Absorbance for all excitation wavelengths from analysis",
  "with an Aqualog multispectral fluorometer"
);

metaEnv$tableAbsorbance.meta <- data.frame(
  dateString = atts$date,
  siteID = atts$siteID,
  repID = atts$repID,
  wavelength = atts$eemsExcitationWavelength,
  absorbance = atts$absorbance,
  row.names = rownames(atts)
);

```

`r sprintf("**%s.csv**", metaEnv$tableAbsorbance.name)`: `r metaEnv$tableAbsorbance.desc`

`r knitr::kable(x = metaEnv$tableAbsorbance.meta) `


## Table of summary absorbance and fluorescence metrics

```{r}

df <- read.table(
  file = "./03_incremental/LTREB_OpticalProp_Aqualog_ WY_2018 _FINAL.txt",
  sep = "\t",
  header = TRUE
);

dates <- as.POSIXct(
  df$DATE,
  format = "%Y-%m-%d",
  tz = "UTC"
);
metaEnv$startTime <- min(metaEnv$startTime, dates);
metaEnv$endTime <- max(metaEnv$endTime, dates);

df$dateString <- format(
  x = dates,
  format = "%Y%m%d"
)

df$siteID <- sprintf(
  "%03d",
  as.numeric(substr(df$SITE, 2, 3))
)

df$repID <- substr(df$REP, 2, 2);

metaEnv$tableSummaryMetrics.name <- "Summary_metrics_wy2018";

metaEnv$tableSummaryMetrics.desc <- paste(
  "Summary metrics of absorbance and fluorescence including",
  "the absorbace at 254nm, fluorescence index, and humification index"
);

metaEnv$tableSummaryMetrics.meta <- data.frame(
  dateString = atts$date,
  siteID = atts$siteID,
  repID = atts$repID,
  abs_254nm = atts$abs254,
  FI = atts$fluorIndex,
  HIX = atts$humificationIndex,
  row.names = rownames(atts)
);

table <- df[names(metaEnv$tableSummaryMetrics.meta)]

```

`r sprintf("**%s.csv**", metaEnv$tableSummaryMetrics.name)`: `r metaEnv$tableSummaryMetrics.desc`

`r knitr::kable(x = metaEnv$tableSummaryMetrics.meta) `

```{r}

# Write the data table to the product

write.csv(
  x = table,
  file = sprintf(
    "%s/%s.csv",
    productPath,
    metaEnv$tableSummaryMetrics.name
  ),
  row.names = FALSE
)

```


## Write metdata object

```{r}

# Specify the path to the temporary metadata file and write
# the metadata environment to it

file <- sprintf(
  "%s/metadata.RData",
  tempPath
);
saveRDS(
  object = metaEnv,
  file = file
)

```

Temporary metadata file written to `r file `


## Summary of R session used to compile this Rmarkdown

```{r results = "markup"}

# Render the session information

print(sessionInfo()) 

```
